Inferring generation-interval distributions from contact tracing data

### 2018-09-26 doc/network.tex
Autocommit (doc)

\documentclass{article}
\title{Inferring generation-interval distributions from contact tracing data}
\author{Sang Woo Park, David Champredon and Jonathan Dushoff}

@@

Aggregating generation intervals across heterogeneous environment also affects the observed generation intervals.
Infection is more likely to spread quicker than on average among closely related inidividuals, and the local decrease in susceptibles result in shorter realized generation intervals.
\cite{trapman2016inferring} gave a similar argument to explain the difference in the the reproductive numbers between a homogeneously mixing population and a heterogeneously (network structured) mixing population.
Their result can be interpreted as a consequence of changes in generation-interval distributions: shorter generation intervals lead to smaller reproductive number [CITE].

@@

\subsection*{Right-censored interval}

>>>>

\documentclass[12pt]{article}
\title{Inferring generation-interval distributions from contact tracing data}
\author{Sang Woo Park, David Champredon and Jonathan Dushoff}

@@

Aggregating generation intervals across heterogeneous environment also affects the observed generation intervals.
Infection is more likely to spread quicker than on average among closely related individuals, and the local decrease in susceptibles result in shorter realized generation intervals. \jd{Not following, and not sure we want to go here for now.}
\cite{trapman2016inferring} gave a similar argument to explain the difference in the the reproductive numbers between a homogeneously mixing population and a heterogeneously (network structured) mixing population.
Their result can be interpreted as a consequence of changes in generation-interval distributions: shorter generation intervals lead to smaller reproductive number [CITE].

@@

\subsection*{Right-censored intervals}
